---
title: "3D Plot of Movie Data"
author: "Irene Chen"
date: "2/25/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## IMDb Movie Data
- The plot on the next slide displays movie data taken from IMDb. 
- The x-axis shows the movie release year (between 1980 and present), the y-axis shows the IMDb rating for the movie, and the z-axis shows the total number of crew working on the movie. 
- The bubble size and color reflect how much money the movie made (movie gross, not profit). 
- Mouse over the bubbles to view the title of the movie!

## 3D Plot of Movie Data 

```{r, echo=FALSE, message=FALSE}
library(plotly)
file <- list.files(pattern="moviedf.csv", full=TRUE)
df <- read.csv(file, header=TRUE, sep=",")
movie_plot <- plot_ly(y=df$year, x=df$rating, z=df$num_crew, mode="markers", marker=list(size=df$gross, sizeref=15), color= ~df$gross, text = ~paste(df$title))
layout(movie_plot, title="3 Decades of Animated Movies", scene=list(xaxis=list(title="IMDb rating", range=c(4,9)), yaxis=list(title="year"),
                                               zaxis=list(title="crew size")))
```

